Results

### 2023-03-31 06_Paper/ER-ED/ERED_Stage2/Results.Rmd
corrected percentage of variance

To investigate, which variables can predict individual SVs of ER strategies, a multilevel model approach was chosen.
The ICC of the null model was $ICC=$ `r papaja::printnum(ICC_between_MLM_0)`, indicating that the level-2 predictor subject accounted for `r papaja::printnum(round(ICC_between_MLM_0*100, digits = 1))`% of total variance.
The preregistered model showed a correlation of $r=$ `r papaja::printnum(attr(summary(MLM_1)$varcor[1]$ID,"correlation")[1,2])` of the random effects subjects and recoded strategy ($BF10$ of the variable strategy: `r papaja::apa_print(MLM_1_BF)$statistic`).
Our model explained `r papaja::printnum(MLM1_r2[2])`% of variance and thus we assumed our model was overfitted due to including recoded strategy as the random slope.
We therefore set a new model without the recoded strategy as the random slope factor to estimate the influence of predictors on SVs more precisely.
The second model followed the specification: 
$$
\begin{split}
SV \sim \text{effort rating} + \text{arousal rating} + \text{utility rating} + corrugator \text{ activity} \\\ + levator \text{ activity} + (1 |subject)
\end{split}
$$

The second model explained `r papaja::printnum(MLM2_r2[2])`% of variance. 
All results of the second model are in Table\ \@ref(tab:TabMLMH5).

>>>>

To investigate, which variables can predict individual SVs of ER strategies, a multilevel model approach was chosen.
The ICC of the null model was $ICC=$ `r papaja::printnum(ICC_between_MLM_0)`, indicating that the level-2 predictor subject accounted for `r papaja::printnum(round(ICC_between_MLM_0*100, digits = 1))`% of total variance.
The preregistered model showed a correlation of $r=$ `r papaja::printnum(attr(summary(MLM_1)$varcor[1]$ID,"correlation")[1,2])` of the random effects subjects and recoded strategy ($BF10$ of the variable strategy: `r papaja::apa_print(MLM_1_BF)$statistic`).
Our model explained `r papaja::printnum(MLM1_r2[2]*100, digits=1)`% of variance and thus we assumed our model was overfitted due to including recoded strategy as the random slope.
We therefore set a new model without the recoded strategy as the random slope factor to estimate the influence of predictors on SVs more precisely.
The second model followed the specification: 
$$
\begin{split}
SV \sim \text{effort rating} + \text{arousal rating} + \text{utility rating} + corrugator \text{ activity} \\\ + levator \text{ activity} + (1 |subject)
\end{split}
$$

The second model explained `r papaja::printnum(MLM2_r2[2]*100, digits=1)`% of variance. 
All results of the second model are in Table\ \@ref(tab:TabMLMH5).
